---
title: "Example Microaray"
author: "Andrew Burr"
date: "March 30, 2017"
output: html_document
---


```{r libraries&data, echo = FALSE, warning=FALSE}

# Load libraries
library(knitr)
library(edgeR)
library(biomaRt)
library(ggplot2)
library(beadarray)
library(limma)
library(illuminaHumanv4.db)
library("simpleaffy")
library("affyQCReport")
library(annotate)
require(reshape)
#library("lumi")


#creates an expression set from microarray data for analysis with limma
createExpressionSet <- function(projectFolder ){
# Load data
## location of your probe and qc files
dataFile <- paste(projectFolder, "Data/SampleProbeProfile.txt", sep="")
qcFile <-   paste(projectFolder,"Data/ControlProbeProfile.txt", sep="")
## create an expressionset
eset <- readBeadSummaryData(dataFile=dataFile, qcFile=qcFile,
                            ProbeID="PROBE_ID", controlID="ProbeID",
                            skip=0, qc.skip=0,
                            annoCols=c("SYMBOL", "DEFINITION", "SYNONYMS", "CHROMOSOME", "ILMN_GENE", "SEARCH_KEY"))

#plot(eset, what = "lumi::boxplot", logMode = FALSE)

# Normalize, transform
eset <- normaliseIllumina(eset, method="quantile", transform= "log2")

# Some of limma's stuff downstream doesn't work with whatever kind
# of object that you get out of normaliseIllumina().
# I coerce it to an "ExpressionSet" and everything seems to work fine.
class(eset) <- "ExpressionSet"

return(eset)

# Analyze with limma
## Make a design matrix
## Make a contrast matrix
## analyze the normal way: lmFit(), contrasts.fit(), eBayes(), topTable()
}



getGeneResults <- function(results, fit, line){
  
significant_rows <- apply(abs(results), MARGIN =  1, FUN = sum) >= 1 
probe_conversion <- subset(select = c(ProbeID, SYMBOL),
                 x = topTable(fit[significant_rows,],
                              number = "all",
                              lfc = lfc, 
                              p.value = .05)
                 )
results <- as.data.frame(results)
results$ProbeID <- rownames(results)
results_table <- merge(results, probe_conversion, by = "ProbeID")
rownames(results_table) <- results_table$ProbeID
results_table <- subset(results_table, select = -ProbeID)
results <- subset(results, select = -ProbeID)
colnames(results_table) <- c(paste(colnames(results), line, sep ="_"), "SYMBOL")
return(results_table)
}
```

```{r variable_setup}

lfc <- 1
```

**EXAMPLE**



```{r cell_line_4121_AE, error=T}

#DESIGN OF THE EXPERIMENT
`cell_`=factor(c(rep("shNT", 4), rep("shA", 4), rep("shE",4)), levels = c("shNT", "shA", "shE"))
design <-model.matrix(~`cell_` + 0)
rm('cell_')

#convert the probe data to an illumina ExpressionSet required for analysis
c4121_ES_AE <- createExpressionSet("../Experiments/Cell_Line_4121_AE/")



#mds Plot of the cell lines
#cell lines are placed based on typical distances of the top log2 fold changes
plotMDS(c4121_ES_AE, labels = designArray, cex = .7)

#doing a linear fit of the data
fit_c4121L <- lmFit(c4121_ES_AE, design)
#creating the contasts, the differences, between each cell type
contrasts <- makeContrasts(cell_shA-cell_shNT, cell_shE-cell_shNT, levels = design)
fit_c4121L <- contrasts.fit(fit_c4121L, contrasts)
fit_c4121L <- eBayes(fit_c4121L, trend = TRUE)


#find probes with at least 1 log fold change difference in shNT vs both shA and shE and put in a venn diagram
results <- decideTests(fit_c4121L[, c("cell_shA - cell_shNT", "cell_shE - cell_shNT")], 
                       lfc = lfc, 
                       p.value = .05)
#create a venn diagram showing the number of  up and down regulated probes
vennDiagram(results, 
            include = c("up", "down"), 
            names = c("shA-shNT","shE-shNT"))


A_4121_top <- subset(select = -c(CHROMOSOME,ILMN_GENE,SEARCH_KEY, Status, P.Value),topTable(fit_c4121L, coef = 1,sort.by = "p", number = "all", lfc = lfc, p.value = .05))


E_4121_top <- subset(select = -c(CHROMOSOME,ILMN_GENE,SEARCH_KEY, Status, P.Value),topTable(fit_c4121L, coef = 2,sort.by = "p", number = "all", lfc = lfc, p.value = .05))
